---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LibLabReviews

<!-- badges: start -->
<!-- badges: end -->

The goal of LibLabReviews is to provide a toolset that enables easier, more standardized and more effective peer reviews in a data science setting. Given a project, the tools provided make pull requests, issue creation and other part of peer review easier and provide templates with learnings from other review processes.

## Installation

LibLabReviews will be installed as a part of installation of `LibLabs` so should typically not be installed alone. However, if you do want to install alone for a specific reason (eg different release versions), you can do so by following the instructions for the installation of any private `LibLabs` package.

``` r
remotes::install_github('aclu-national/LibLabReviews')
```

## Usage

Most users are unlikely to use the features of this package directly. It will be included in any future project installs. Howevers, the core function is `use_aclu_review_template` which adds files to your repository that will be useful for future code reviews.

```{r example, eval=FALSE}
library(LibLabReviews)
use_aclu_review_template()
```

Once this has run, anytime you choose to file either an issue or a pull request, it will provide a template / checklist to support the process for you.
